Report - Latest Rodent Data

### 2018-02-02 report.Rmd
Update report.Rmd
select & pull are redundant
adding dplyr namespace for pull

# get new moon number associated with this period
newmoons_table = read.csv(text = getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))
newmoons_table$censusdate = as.Date(newmoons_table$censusdate,format='%Y-%m-%d')
moon_code = dplyr::filter(newmoons_table,period==most_recent_period) %>% select(newmoonnumber) %>% as.integer()
most_recent_date = dplyr::filter(newmoons_table,period==most_recent_period) %>% dplyr::select(censusdate)

>>>>

# get new moon number associated with this period
newmoons_table = read.csv(text = RCurl::getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))
newmoons_table$censusdate = as.Date(newmoons_table$censusdate,format='%Y-%m-%d')
moon_code = dplyr::filter(newmoons_table,period==most_recent_period) %>% select(newmoonnumber) %>% as.integer()
most_recent_date = dplyr::filter(newmoons_table,period==most_recent_period) %>% dplyr::pull(censusdate)
